Our Title

### 2015-05-08 draft.tex
Added in "People" subsection to the Introduction chapter.

@@

\begin{itemize}
\item \textbf{Illicit proceeds from occupation of territory, including oil, extortion, and bank looting:} ISIL's sophisticated extortion racket is similar to that of organized crime rings. ISIL uses force to gain and control resources, including banks, oil and phosphates, agriculture, and archeological sites \cite{Report2015}.
\item \textbf{Kidnapping for ransom:} Reports indicate that ISIL has kidnapping hundreds of people, including Iraqis, Syrians, local ethnic minorities, Westerners, and East Asians. While ISILs murdering of hostages was garnered widespread attention, they have also been effective in extracting ransom payments, with revenue estimated between \$20 million and \$45 million USD \cite{Report2015}.
\item \textbf{Donations:} While revenue from external donations has been a relatively small portion of ISIL's income, it has recently been growing in importance. In addition to donations from the Gulf, there is also risk that wire transfers to charitable foundations operating in ISIL territory end up in ISIL's hands \cite{Report2015}. 
\item \textbf{Material support from foreign fighters:} In some instances, foreign terrorist fighters collect money in their home countries and uses it to provide monetary support to ISIL \cite{Report2015}.
\item \textbf{Online fundraising:} While fundraising through modern communications networks is a relatively small  piece of ISIL's income, the group has shown a strong ability to use social media sites such as Twitter and online crowd funding to support its operations \cite{Report2015}.
\end{itemize}

@@

\subsection{How does this relate to their potential nuclear interests?}
\subsubsection{????? Missing ?????}
\subsubsection{????Move in info from mat / signatures group????}

we can pull from what the State Department is already doing on this

@@

\subsection{????????  Needs expansion  and references   ????????????}

>>>>

ISIL has as many as 31,500 fighters in Iraq and Syria, and roughly 19,000 of these are foreign recruits from 90 countries \cite{Sengupta2014,TheEditorialBoard2015}. ISIL has called publicly on Muslims from the world over to join the Caliphate as part of their religious duty as true believers \cite{Stern2015}. In order to recruit foreign fighters - who are often more ideological than the average Syrian rebel - ISIL propaganda is frequently translated into English, French, German, Russian, Indonesian, Urdu, and other languages \cite{Stern2015}. ISIL also recruits through sophisticated modern communication techniques and through representatives in countries around the world in Muslim diaspora populations \cite{Masi2014}.  The majority of foreign fighters originate in Muslim countries in the Middle East and North Africa, with especially high representation from Tunisia and Saudi Arabia. A typical foreign ISIL fighter is a male between the ages of 18 and 29, but may be as young as 15 \cite{Stern2015}.

ISIL also recruits heavily from the West. The U.S. State Department knows of dozens of U.S. citizens fighting for ISIL, and the British government estimates that roughly 500 British citizens have become foreign fighters in ISIL's ranks \cite{Masi2014a}.  In order to join ISIL, recruits from the west must have a jihadi mentor, which can be found online through ISIL's media center or through ISIL supporters in their communities \cite{Masi2014a}.  Many of these western recruits have entered ISIL territory through Turkey \cite{Masi2014a}.  These western terrorist fighters raise concerns that they will return home radicalized and attempt to attack the U.S. homeland \cite{Patrick2014}.

Decades of psychological research have failed to produce a profile of who becomes a terrorist \cite{Stern2015}. Despite this, there are several pathways to becoming a foreign jihadist, with both internal and external motivations. Foreign terrorist fighters often mention as external motivations specific military conflicts that inspired them to join terrorist groups. Internal motivations include a sense of belonging, the opportunity to take on a new identity, adventure, or money \cite{Stern2015} Recent ISIL video propaganda films demonstrate a startling level of production value that may indicate that the group is recruiting and possibly paying individuals with specialized skills. Taken together, these findings demonstrate that ISIL attracts not only fighters, but also individuals with specialized skills sets, and it does so through both payment and through cultivating a sense of belonging for Muslim immigrants in Western countries and throughout the world \cite{Patrick2014}.

@@

\begin{itemize}
\item \textbf{Illicit proceeds from occupation of territory, including oil, extortion, and bank looting:} ISIL's sophisticated extortion racket is similar to that of organized crime rings. ISIL uses force to gain and control resources, including banks, oil and phosphates, agriculture, and archeological sites \cite{Report2015}.
\item \textbf{Kidnapping for ransom:} Reports indicate that ISIL has kidnapping hundreds of people, including Iraqis, Syrians, local ethnic minorities, Westerners, and East Asians. While ISILs murdering of hostages was garnered widespread attention, they have also been effective in extracting ransom payments, with revenue estimated between U.S. \$20 million and \$45 million \cite{Report2015}.
\item \textbf{Donations:} While revenue from external donations has been a relatively small portion of ISIL's income, it has recently been growing in importance. In addition to donations from the Gulf, there is also risk that wire transfers to charitable foundations operating in ISIL territory end up in ISIL's hands \cite{Report2015}. 
\item \textbf{Material support from foreign fighters:} In some instances, foreign terrorist fighters collect money in their home countries and uses it to provide monetary support to ISIL \cite{Report2015}.
\item \textbf{Online fundraising:} While fundraising through modern communications networks is a relatively small  piece of ISIL's income, the group has shown a strong ability to use social media sites such as Twitter and online crowd funding to support its operations \cite{Report2015}.
\end{itemize}

@@

@@
